---
title: "Forecast Report"
author: "Ryan J. Price"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(stlfedR)
library(forecast)

fred_id <- readRDS(file.path(here::here(), "fred_id.rds"))
fcast <- readRDS(file.path(here::here(), "fcast.rds"))
fcast_dates <- rownames(as.data.frame(fcast))
fcast_dates <- list(first = fcast_dates[1], last = fcast_dates[length(fcast_dates)])
```

Forecast for FRED Data
----------------------

According to the latest data available for Federal Reserve Economic Data ID '`r fred_id`',
the forecasted data from `r fcast_dates$first` to `r fcast_dates$last` is as
follows:

```{r fcast_plot, echo=FALSE}
plot(fcast)
```

```{r insights, echo=FALSE}
mape <- round(accuracy(fcast)[5], 1)
fcast_data <- as.numeric(fcast$mean)
model_data <- data.frame(fcast = fcast_data, trend = 1:length(fcast_data))
trend <- coef(lm(fcast ~ trend, data = model_data))[2]
if (sign(trend) == 1) {
    trend <- list(desc = "positive", chgword = "increase")
} else {
    trend <- list(desc = "negative", chgword = "decrease")
}
delta <- round(abs(tail(fcast_data, 1) - head(fcast_data, 1)), 1)
```

The MAPE (Mean Absolute Percentage Error) for this forecast is approximately `r mape`%.

You can see that the projection has a `r trend$desc` trend, with an overall `r trend$chgword`
of `r delta` {UNITS OF FRED_ID} during the forecast period.
